**Preprinting Microbiology**

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Correct typo, Close #8

As the total number of preprints has grown exponentially since the creation of *bioRxiv*, submission of microbiology-affiliated preprints has largely followed this growth (**Figure 1A**). Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity. Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated preprint (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints. Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r round(micro_aff_countries_percent[1], 1)`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r round(micro_aff_countries_percent[2], 1)`%), and `r micro_aff_countries_names[3]` (`r round(micro_aff_countries_percent[3], 1)`%). As the preprint format matures, it will be interesting to see whether the fraction of authors that post multiple preprints increases and whether the geographic diversity amongst those authors is maintained.

>>>>

As the total number of preprints has grown exponentially since the creation of *bioRxiv*, submission of microbiology-affiliated preprints has largely followed this growth (**Figure 1A**). Although preprints are still relatively new, the collection of microbiology-affiliated preprints indicates widespread experimentation with the format and considerable geographic diversity. Reflecting the relative novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r round(100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts), 1)`%) corresponding authors who submitted a microbiology-affiliated preprint (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r round(100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts), 1)`% have posted 3 or more preprints. Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r round(micro_aff_countries_percent[1], 1)`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r round(micro_aff_countries_percent[2], 1)`%), and `r micro_aff_countries_names[3]` (`r round(micro_aff_countries_percent[3], 1)`%). As the preprint format matures, it will be interesting to see whether the fraction of authors that post multiple preprints increases and whether the geographic diversity amongst those authors is maintained.
